Unrecognized States: Theory and Cases

### 2017-07-04 theory.tex
first pass at cutting down sanctions section

\textbf{<<COMP: Place Figure 1 about here>>}

@@

Let us begin with the simplest case, in which the sanctions affect only the secessionists' status quo payoffs, as when the imposition of sanctions has a negative impact on the economy of the unrecognized state. We assume sanctions have only two effects: to narrow the difference between the payoffs from Status Quo and Fight, and to narrow the difference between the payoffs from Status Quo and Cede. If the patron wishes to maintain the status quo, its per-period investment must increase to compensate for the additional degradation of the status quo payoffs caused by the sanctions. In this case, the effect of sanctions on the unrecognized state's choice is ambiguous. Proposition 2 lists necessary conditions for the existence of an equilibrium in which ``ceding'' is the equilibrium outcome once sanctions are introduced.

@@

Thus, even if we do not consider the sanctions to impose any direct costs on the home state (though in practice they likely do), it remains ambiguous whether sanctions will benefit the home state. Recall that in the Status Quo Equilibrium, the home state's expected returns from war are lower than from a continuation of the status quo. If sanctions induce the secessionists to play Fight, this is a worse outcome for the home state than if the status quo had been allowed to persist.

Moving beyond this simple case, we can add realism by allowing sanctions to have a negative effect not only on the economy (the status quo payoffs) but also on the military capabilities of the secessionists (the expected payoffs from war). This is an important extension because one motivation for sanctions is often precisely that -- to weaken the military capability of the secessionists.

In the model, this is represented as reducing (increasing) the secessionists' probability of victory (loss) in the war lottery. This should serve to increase the range of parameters over which the conditions of Proposition 2 hold. However, at the same time, the home government experiences changes of the same magnitude and opposite sign in its war lottery, increasing its payoffs from playing Fight. The effect of sanctions on the home state's strategic considerations is clear cut:

@@

The proof of Proposition 3 is immediate. Although under the conditions of Proposition 1 (i.e., when the restriction of Definition 1 hold and the Status Quo Equilibrium is played) the home state's continuation value from maintaining the status quo is higher than from initiating conflict in the absence of sanctions, when those sanctions degrade the secessionists' military capabilities they increase the chances that the home state would prevail in a conflict, thus increasing the home government's continuation value from fighting. The stronger is the impact of sanctions on the secessionists military, the stronger is the effect on the home government's value of fighting and the greater is the range of parameters over which this change in payoffs will lead to a change in behavior.

@@

\newpage

>>>>

@@

Let us begin with the simplest case, in which the sanctions affect only the secessionists' status quo payoffs, as when the imposition of sanctions has a negative impact on the economy of the unrecognized state. In this case, the effect of sanctions on the unrecognized state's choice is ambiguous.

@@

We can add realism by allowing sanctions to have a negative effect not only on the economy (the status quo payoffs) but also on the military capabilities of the secessionists (the expected payoffs from war). This is an important extension because one motivation for sanctions is often precisely that -- to weaken the military capability of the secessionists.

In the model, this is represented as reducing the secessionists' probability of victory in the war lottery. This should serve to increase the range of parameters over which the conditions of Proposition 2 hold. However, at the same time, the home government experiences changes of the same magnitude and opposite sign in its war lottery, increasing its payoffs from playing Fight.

@@

It is immediate that the stronger is the impact of sanctions on the secessionists military, the stronger is the effect on the home government's value of fighting and the greater is the range of parameters over which this change in payoffs will lead to a change in behavior.

@@
